A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Acknowledgements
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1008 43ef1190-90fd-4dd7-a769-d0121f02b80e

To see if the server actually supported conditional requests, and not
just merely set the response headers, we made another 1822 requests to
the resources that had these headers. Then, we checked if the response
code was 200, and the conditional headers had not changed since our
initial requests. In 85 cases, conditional requests were not supported
according to the standard, no cases for endpoints, 3 for datasets and
23 for vocabularies, 59 for generic information resources.\todo{table instead?}

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Axel Polleres for inspiring me to start this study, to
Martin Giese for careful review and critical comments, and Gregory
Todd Williams for promptly solving issues in the underlying libraries
used in this study.

>>>>

To see if the server actually supported conditional requests, and not
just merely set the response headers, we made another 1822 requests to
the resources that had these headers. Then, we checked if the response
code was 200, and the conditional headers had not changed since our
initial requests. In 85 cases, conditional requests were not supported
according to the standard, no cases for endpoints, 3 for datasets and
23 for vocabularies, 59 for generic information resources.

@@

\paragraph*{Acknowledgements} The author would like to thank Jürgen
Umbrich and Martin Giese for careful review and critical comments, and
Gregory Todd Williams for promptly solving issues in the underlying
libraries used in this study, and Axel Polleres for encouraging comments.
